\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2018-06-26 eg6-letters/NIM/EG6_RTPC_NIM.tex
Changes for submission of NIM on Arxiv and NIM
Modification asked by reviewer
some cleaning

\documentclass[preprint,5p]{elsarticle}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}  
\usepackage{textcomp}  
\usepackage{amssymb}  
\usepackage{hyperref}
\providecommand{\keywords}[1]{\textbf{\textit{Keywords:}} #1}
\hypersetup{colorlinks=true, urlcolor=blue, citecolor=blue}
\usepackage[displaymath]{lineno}
\linenumbers
\usepackage{dblfloatfix}    % To enable figures at the bottom of page
\begin{document}

@@

\begin{figure}[tbp]
\centering \includegraphics[scale=0.3]{test_clas.png}
\caption{A three dimensional representation of the baseline CLAS setup. The
   full description is given in the text.} \label{fig:CLAS}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics[scale=0.70]{GEM_photo.jpg}
\caption{Image of a typical GEM foil similar to the one used for our RTPC 
\cite{Sauli:2016eeu}.} 
   \label{fig:GEMs}
\end{figure}

@@

\begin{figure}[tb]
   \centering
   \includegraphics[scale=0.55]{PADs.png}
   \caption[]{A schematic representation of the readout pads. The 
   shaded sixteen pads are a group of pads that are connected to the same 
pre-amplifier.} \label{fig:PADs}
\end{figure}

@@

The first step in the calibration is to fix the maximum drift time ($T_{max}$) that an
electron can arrive on the detection plane. This value is highly dependent on the gas 
mixture composition, as well as the electric and magnetic field experienced by the drift 
electrons. The maximum time corresponds to electrons released close to 
the cathode, which are the furthest from the readout pads as illustrated in 
Figure~\ref{fig:RTPC_signals}. Note that the minimum time is not calibrated, as we
use the trigger time for it ($T_{min}=15$), and that the time unit is the ALTRO 
sampling time of 100~ns.

@@

\begin{figure}[tb]
   \centering
\includegraphics[scale=0.25]{noisy_pad_before_rejection2.png}
\includegraphics[scale=0.25]{noisy_pad_after_rejection2.png}
\caption{The ADC vs. T spectrum for an example noisy channel before (top) and 
after (bottom) noise rejection algorithms.  Only hits associated with tracks 
are included, and the selection of events and tracks is the same in both 
plots.}
\label{fig:noise}
\end{figure}

>>>>

\documentclass[preprint,5p]{elsarticle}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}  
\usepackage{textcomp}  
\usepackage{amssymb}  
\usepackage{hyperref}
\providecommand{\keywords}[1]{\textbf{\textit{Keywords:}} #1}
\hypersetup{colorlinks=true, urlcolor=blue, citecolor=blue}
\usepackage[displaymath]{lineno}
%\linenumbers
\usepackage{dblfloatfix}    % To enable figures at the bottom of page
\begin{document}

@@

\begin{figure}[tbp]
\centering \includegraphics[scale=0.18]{test_clas.png}
\caption{A three dimensional representation of the baseline CLAS setup. The
   full description is given in the text.} \label{fig:CLAS}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics[scale=0.17]{GEM_photo.jpg}
\caption{Image of a typical GEM foil similar to the one used for our RTPC 
\cite{Sauli:2016eeu}.} 
   \label{fig:GEMs}
\end{figure}

@@

\begin{figure}[tb]
   \centering
   \includegraphics[scale=0.21]{PADs.png}
   \caption[]{A schematic representation of the readout pads. The 
   shaded sixteen pads are a group of pads that are connected to the same 
pre-amplifier.} \label{fig:PADs}
\end{figure}

@@

The first step in the calibration is to determine the maximum drift time ($T_{max}$) at which an
electron can arrive on the detection plane. This value is highly dependent on the gas 
mixture composition, as well as the electric and magnetic field experienced by the drift 
electrons. The maximum time corresponds to electrons released close to 
the cathode, which are the furthest from the readout pads as illustrated in 
Figure~\ref{fig:RTPC_signals}. Note that the minimum time is not calibrated, as we
use the trigger time for it ($T_{min}=15$), and that the time unit is the ALTRO 
sampling time of 100~ns.

@@

\begin{figure}[tb]
   \centering
\includegraphics[scale=0.20]{noisy_pad_before_rejection2.png}
\includegraphics[scale=0.20]{noisy_pad_after_rejection2.png}
\caption{The ADC vs. T spectrum for an example noisy channel before (top) and 
after (bottom) noise rejection algorithms.  Only hits associated with tracks 
are included, and the selection of events and tracks is the same in both 
plots.}
\label{fig:noise}
\end{figure}
